Which ITG Stepcharts are Turniest?

### 2019-03-15 itg/3/paper.tex
start writing overview

\conferenceinfo{SIGBOVIK '17}{Pittsburgh, PA, USA}
\copyrightyear{2017}
\copyrightdata{}

@@

\authorinfo{Ben Blum}{}{bblum@cs.cmu.edu}

@@

\keywords
brackets, jumps, bracket jumps

@@

\begin{figure}[h]
	\hspace{-2em}\includegraphics[angle=270,width=0.54\textwidth]{../2/paper.pdf}
	\caption{(yeah i reused this joke from last time ok deal)}
	\label{fig:you-stutid-fuckass}
\end{figure}

@@

>>>>

\conferenceinfo{SIGBOVIK '19}{Pittsburgh, PA, USA}
\copyrightyear{2019}
\copyrightdata{}

@@

\authorinfo{Ben Blum}{}{bblum@alumni.cmu.edu}

@@

\keywords
bracket, groove, in, jumps, the

@@

\begin{figure}[t]
	\hspace{-2em}\includegraphics[angle=270,width=0.54\textwidth]{../2/paper.pdf}
	\caption{(yeah i reused this joke from last time ok deal)}
	\label{fig:you-stutid-fuckass}
\end{figure}

\section{Overview}

% TODO: go through this paper and make every *other* instance of "bracket-jump" hyphenated

What, then, is a bracket jump (which I shall \textit{not}, henceforth, abbreviate for brevity)?
Put simply, whenever two arrow-shaped obstacles proceed simultaneously towards the protagonist directional indicator targets
(see \cite{turniness}),
while a novice player might think they must step with both feet at once, one for each arrow,
experts often find it more convenient (i.e., less overall foot motion) to use whichever single foot is closer at the time
to hit both arrows by stepping across the metal bracket enclosing the corners of each panel
(thereby triggering one sensor with the heel and one with the little bitty toesies), hence ``bracket jump''.
In case my verbal explanation is not up to snuff, I have also included in \Cref{fig:how-2-bracket}
a high-quality graphics render of a player's typical foot positions during a down+right bracket jump (henceforth ``DR'', et cetera).

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.48\textwidth]{how-2-bracket.jpg}
	\end{center}
	\caption{Down+right bracket jump real-world example.}
	\label{fig:how-2-bracket}
\end{figure}

@@

% TODO tings to talk about

% authors seem to know it's easy to overdo -- see, "Stupid" and "I'm sorry" as chart authors in some of the top charts

% many old charts written without regard to jump patterning can be bracker anyway, see OWA (which just makes the list bc it's long)
% - have a figure of OWA in the strema that shows the *non* bracketable stream jumps
% - make a test case that captures these and shows indeed they are not brackets

% temporal analysis of pack age vs bracker density

% other charts of note
% - chicago timing / electrical paradise: bracketiest chart where *ALL* jumps are brackets (BJJ%=100) -- quite tasteful actually!
% - encore is 2nd place lmao

% conclusion: BJJ% is sa better measure of chart funness than BJS%?
